\chapter{System Description}\label{SystemDescription}
As a part of this semesters requirements, the developed product must take the
form of an embedded systems. In addition, the system must also make use of the
techiques taught in either the 'Real Time Systems (RTS)' course, or the 'Machine
Intelligence (MI)' course. As none of the group's participants are partaking in
the RTS course, this project will be focused on the techniques and models taught in
the MI course. In order to implement these techniques we will need to gain a
deeper understanding of these concepts. As such, this chapter will be used to
describe what an embedded system is, how real-time systems incorporate deadlines
and schedules and examine what elements from machine intelligence can be used
by an autonomous turret.

\section{Embedded Systems}
As explained by the embedded systems manufacturer BarrGroup
\citep{Barr_Embedded}, an embedded system can be defined as: \nl

\begin{center}
\begin{minipage}{0.8\linewidth}
\say{A combination of computer hardware and software, and perhaps additional
mechanical or other parts, designed to perform a dedicated function. In some
cases, embedded systems are part of a larger system or product, as in the case
of an antilock braking system in a car.}
\end{minipage}
\end{center}
% An embedded system is a device with limited resources both in terms of computing
% power and how much memory it has available. They are used everywhere to do small
% task and jobs. \fix{It is difficult to give an exact definition of what an
% embedded system is, but a crude definition\citep[ch.1.1]{vahid1999embedded}
% is}{We need a better definition}:\nl
% 
% \textit{An  embedded  system  is  nearly  any computing system other than a desktop,
% laptop, or  mainframe  computer.}\nl

This means that embedded systems cover alot of different types of systems, for
example the antilock braking system (ABS) in a modern car, the cash registers in
retail stores and washing machines. The requirements can therefore differ alot
between systems, although they do share some characteristics \citep[ch.1.1]{vahid1999embedded}:

\begin{enumerate}
  \item \textbf{Single-functioned}: Most embedded systems only have a single
  purpose, running the same program over and over again. An example could be a
  washing machine. The computer inside it will always have the same
  function (control the washing machine), and although it might have a variety
  of different programs to execute (wool, synthetics, different temperatures),
  it is still considered single-functioned.
  \item \textbf{Tightly constrained}: All systems have some limits, but embedded
  systems are much more tightly constrained when it comes to cost, size,
  performance and power. These are to be understood as a compromise between the
  different aspects, for example it could be impossible to make the embedded
  system smaller without making it more expensive.
  \item \textbf{Reactive and real-time}: Many embedded systems have to react to
  some kind of external stimuli. If an embedded system has to take into account
  this external dyniamic information, it is considered a real-time system. We
  will further expand upon what this means in \autoref{rts}.
\end{enumerate}
