\section{Requirements}

Based on\ldots, we can determine the requirements for an autonomous
turret.
These requirements can further be divided into the groups ``Need to have'' and
``Nice to have'' in order to prioritize between them.

\subsection{Need to have}
The following requirements have been deemed necessary for an autonomous turret:
\begin{itemize}
  \item The turret needs to be an embedded system and incorparate elements from
  the courses MI and RTS. This is necessary as it is required by the semester.
  \item The turret needs to be able turn a minimum of 90 degrees. Since the
  turret should monitor an area and be able to hit a moving target, it needs to
  be able to turn. If it is not able to turn, line of sight as well as the
  timing in order to hit a target will be severely limited. In regards to how
  far it should be able to turn, a minimum is set to 90 degrees, as this will
  provide a decent sized area in front of the turret.
  \item The turret needs to be able to sense a target at a range of atleast
  250cm, since the \fix{current available sensors have a maximum range of
  255cm}{Should be changed depending on max range of optical}, as long as the
  lighting is good and the target is suitable.
  \item The turret needs to be able to search for targets, as otherwise it would
  have to wait for a target to move into its line of sight. This would limit
  the window of time the turret has in order to hit the target.
  \item The turret should have a maximum firing range of atleast 250cm. This
  number is determined by the maximum sensor range as well as the maximum of
  the design. It can be argued that it could be useful to shoot further than
  what the turret can see, but this is not a necessary feature.
  \item The turret needs to be able to reliably hit a moving target with a
  constant speed atleast 60\% of the time. The turret needs to be able to hit a
  moving target, it is not enough to hit the target sometimes, the turret should
  be able to hit it reliably. The speed should be fast enough to cause the
  turret to miss it, if the turret fires once it is in front of it.
  \item The turret needs to be able to predict where the target will be at a given point
in time. This is necessary as it would otherwise be very unlikely that the
turret would be able to hit the target.
  \item The turret needs to be able to determine the direction, distance
  and speed of the target. This requirement is necessary as it would otherwise be impossible to
calculate and predict where the target will be.
  \item The target should be atleast \fix{10cm*10cm}{what is the optimal size?}, as it
would otherwise be too small to be reliably seen by the turret sensors.
  \item The target is able to move at a constant speed of up to 0.8m/s. In order to
have a suitable ratio between the turrets maximum range and the targets
speed, 0.8m/s was chosen as the speed limit.
  \item The target needs to travel on an even plane.
\end{itemize}

\subsection{Nice to have}
The following requirement have been deemed to be less important to the overall
success of the project:
\begin{itemize}
  \item The turret needs to be able to reliably hit a moving target with a
variable speed atleast 60\% of the time. This requirement is for a
more realistic scenario, as it is much more likely for a living target to
change its movement speed. The turret is able to reliably hit a target with a
variable speed.
  \item The turret is able to prioritize between several targets. In a realistic
scenario it would be possible for more than one target to be present. This would
then lead to a need to prioritize the targets, in order to maximize the
amount of targets hit.
  \item The target is able to accelerate and decelerate. In order to make for a
  more realistic scenario, the target should be able to speed up and slow down.
\end{itemize}

\section{Features and Requirements v2}

Based on\ldots, we can determine the features and requirements for an autonomous
turret. These can further be divided into the groups ``Need to have'' and
``Nice to have'' in order to prioritize between them.

\subsection{}
The following features and requirements are necessary for an autonomous turret:
\begin{itemize}
  \item The turret needs to be an embedded system and incorparate elements from
the fields of machine intelligence and real-time systems. This leads to the
following requirement:
\begin{itemize}
  \item The system needs to use to Lego Nxt 2.0 as the embedded system.
\end{itemize}
  \item The Turret needs to be able to hit a moving target. This leads to the
  following requirements:
  \begin{itemize}
    \item In order to allow the turret to easier hit a moving target, it needs
    to be able to turn. 
    \item The turret needs to be able turn a minimum of 90 degrees. Since the
    turret should monitor an area and be able to hit a moving target, it needs
    to be able to turn. If it is not able to turn, line of sight as well as the
    timing in order to hit a target will be severely limited. In regards to how
    far it should be able to turn, a minimum is set to 90 degrees, as this will
    provide a decent sized area in front of the turret.
    \item The turret needs to be able to sense a target at a range of atleast
    250cm, since the \fix{current available sensors have a maximum range of
    255cm}{Should be changed depending on max range of optical}, as long as the
    lighting is good and the target is suitable.
    \item The turret needs to be able to search for targets, as otherwise it
    would have to wait for a target to move into its line of sight. This would
    limit the window of time the turret has in order to hit the target.
  \end{itemize}  
\item The target needs to move fast enough such that the turret is unable to
hit it, without calculating a firing offset.
\end{itemize}

\subsection{Need to Have}
The following requirements have been deemed necessary for an autonomous turret:

Features:                       Requirementss:
Embedded systems                ---> Use nxt

Hit moving targets              ---> Turn
                                ---> Firing offset
                                ---> Sensor
                                ---> Accuracy

Target requires firing offset   ---> Target specs


\subsubsection{Requirements}
\begin{itemize}
  \item The turret needs to be an embedded system and incorparate elements from
the fields of machine intelligence and real-time systems. This is necessary as
it is required by the semester.
  \item The Turret needs to be able to hit a moving target. This requirement is
taken from straight from the project proposal and can be considered vital to the
success of the project.
\item The target needs to move fast enough such that the turret is unable to
hit it, without calculating a firing offset. This requirement is also a taken
straight from the project proposal.
\end{itemize}

\subsubsection{Features}
\begin{itemize}
  \item The turret needs to be able turn a minimum of 90 degrees. Since the
turret should monitor an area and be able to hit a moving target, it needs to
be able to turn. If it is not able to turn, line of sight as well as the
timing in order to hit a target will be severely limited. In regards to how
far it should be able to turn, a minimum is set to 90 degrees, as this will
provide a decent sized area in front of the turret.
\item Firing range
\item Sensing range
\item Accuracy
\end{itemize}
