\section{Tasks}\fix{}{quite a low level walk though}
The developed software is controlled by the execution of a number of
tasks. On the NXT system a task is simply a collection of code which can be
executed on a thread. The turret makes use of four central threads:
\texttt{Main}, \texttt{GetDataAndCalculate}, \texttt{WaitAndFire} and
\texttt{Tracking}.

\subsection{Main}
The execution of the program begins in the \textc{Main} thread, which is shown
in \autoref{MainThread}. First, the library method
\textc{PosRegEnable} is used to enable the motors ability to set
an absolute position using a PID controller. This is used to allow the turret to set its angle instead of simply turning on/off the motor.
The \textc{SetMotorRegulationTime} method is used to determine the
time in which the motor should regulate its angle\fix{}{why 10}. This allows the
turret to move to the target angle in a single \fix{swift motion, and then make
a hard break} when the target angle has been reached. This hard break can cause
stress to the lego, but is not a problem in the current setup.

\begin{minipage}[H]{\linewidth}
\begin{lstlisting}[caption = Entry point for the program execution., label = MainThread] 
task main(){
    PosRegEnable(ROTATE_MOTOR);
    PosRegEnable(ANGLE_MOTOR);
    SetMotorRegulationTime(10);
    NXTCam_Init(CAM_PORT, CAM_ADDR);
    NXTCam_SendCommand(CAM_PORT, CAM_ADDR, 'A');
    NXTCam_SendCommand(CAM_PORT, CAM_ADDR, 'E');
    SetSensorUltrasonic(SENSOR_LEFT);
    SetSensorUltrasonic(SENSOR_RIGHT);
    Precedes(Track,GetDataAndCalculate);
}
\end{lstlisting}
\end{minipage}

On \textbf{lines 5-7} the NXTCam is initialized, and two commands are
sent to the camera. The command on \textbf{line 6} configures the camera
to sort the returned blobs by size, such that the largest blob is the first
element of the returned arrays. \textbf{Line 7} is used to enable the camera,
and start the blob tracking. \textbf{Line 8-9} are used to
initialize the two sensor ports \textc{SENSOR\_LEFT} and
\textc{SENSOR\_RIGHT} as they are used for ultrasonic distance sensors.
Finally, the \textc{Precedes} method is used to initialize the
threads: \textc{Track} and \textc{GetDataAndCalculate}.
