\section{Embedded Systems}
introduction - As most people are probably aware of, computers have become an integral part of our modern society,
and rapidly changing the way we do things. When most people say computers, they talk about the class of computers
known as desktops, laptops, servers and tablets. But there is an entire class of computers surrounding us in much greater numbers,
although their presence is a lot more incognito. The computers are built into larger electronic deviced.
This class of computer systems is also known as Embedded Systems.

What is an embedded system?

Coming up with an exact definition of an embedded system is a hard task, but \citep{vahid1999embedded} gives a crude
definition of a Embedded System as follows: \nl

An  embedded  system  is  nearly  any computing system other than a desktop, laptop, or  mainframe  computer.

Although is definition is very crude, it at least gives a starting point from which embedded systems can be observed.
By examining some common types of embedded systems we can try to further understand these systems.\nl

So what are embedded systems. These can be found in a variety of different electronic devices such as
\begin{itemize}
\item Consumer electronics - calculators, cellphones(smartphones ofc), digital cameras, camcorders, handheld gaming devices
\item Home Appliances - Washing machine, tumbledryer, thermostats, home security systems, and lighting systems(device that controls lights in a home)
\item Office automation equipment - Copymachine, printer, scanner, fax machine
\item Business equipment -
\item Automobiles - There is a lot of embedded systems in a typical car today - the ABS-brakes of a modern car is a very typical
example of not only a embedded system, but also a Real-Time-System, which will be explained later
\end{itemize}



Intro - fluff
What is a embedded system
Types of ES - mission critical(Rts?)
Typical Embedded SYstems - components, microprocessor???
Reliability
Limited Resources(memory, cpu, power consumption etc)


This section will be used to give an give an overview of how machine
intelligence and real-time systems will be used and what an embedded system
is.\\

A embedded system is a device with limited resources both in terms of computer
power and how much memory it has \PS. They are used everywhere to do small task
and jobs \PS.\\

When working with a embedded system there are different problems to overcome
when it comes to how the software needs to be programed and how to work with the
limited resources of the system \PS.\\

% small devices everywhere doing their very own job, having access to limited
% memory and little computing power.
% Comes with its own mix of software, hardware and mechanical parts.
%
%
% problems with with ES(embedded systems)
% noget MI
% Noget RTS
