\chapter{Sensors} \label{sensors}
In order for \name to be able to perceive the world around it, it needs to make
use of sensors. These sensors are used to gather data about the certain aspects
of the surrounding environment such as sound, visuals, temperature and
movement. Because of the importance of correctly choosing and using these
sensors, this chapter will be used to explain, analyze and test the different
sensors which will be used throughout this project.

\section{Sensor Choices}\label{SensorChoice}
Based on the turret's ideal scenario presented in \autoref{ProblemDomain}, it
was determined that the turrets routine should consist of three main phases:
\textbf{scanning, tracking and shooting}. These phases posed the questions of
how the turret should identify a target, measure the distance to the target and then
shoot the target. For the purpose of this project, these questions will be solved using
two main sensors: a camera and a distance sensor. \\
The camera will be able to
identify and track the target, and the distance sensor will measure the
distance to said target. While there are a number of different sensors which
can be classified as ``distance sensors'', we have chosen to use a standard NXT
ultrasonic distance sensor. This was done due to the limited availability of
sensors in stock, and the possibility of waiting a long time for shipping new
sensors.\\
The contestants regarding the choice of camera were between a
``Microsoft Kinect'' and a ``NXTCam v4''. While the Kinect is vastly more
powerful, it poses the problems of being a larger device which could not easily
be placed on a turning turret, and it would need to be connected to a PC in
order to translate its input into useful data. On the other hand, the NXTCam is
less powerful, but it is easily integrated with the LEGO NXT platform and it can
be placed on the turret itself. In the end, we chose to use the NXTCam, as one
of the goals of this semester is to teach us about designing around the
limitations of embedded systems.

% For the purpose of sensing its environment, the turret will need two key
% features: the ability to identify a target, and the ability to measure the
% distance to said target. The identification process will be used to find and
% track a target, and the distance measurement will be used to accurately use the
% formula for projectile motion described in \autoref{ProjMotion} to hit the
% target. These features are implemented using two different sensors. The camera
% sensor is presented and tested below in \autoref{SensorTheory} and the distance
% sensor in \autoref{SensTheoUltra}.

\input{sections/Sensors/Ultrasonic.tex}
\input{sections/Sensors/Camera.tex}

% \input{sections/Sensors/SensorUltrasonicTheory.tex}
% \input{sections/Sensors/SensorUltrasonicTest.tex}
% \input{sections/Sensors/SensorCameraTheory.tex}
% \input{sections/Sensors/SensorCameraTest.tex}
