\subsection{Filling in the tables}
For each speed we want to implement in the model, we need a dataset, based on
the sensor readings from turret. In order to gather datasets a test was
performed. The test was conducted such that the observations were grouped into a
set: each set consists of 3 sensor readings, the first two observations of a set
are used to construct a vector V1 and the last two observations are used to
construct a vector V2. Using this method we end up with a set of vectors based
upon sensor observations, which means we know the values that resulted in the
vector, which will come in handy in the next step.
Next step is to group the resulting vectors according to whether or not it was
deemed a good vector or a bad vector. After going through the vectors for each
speed, we end up with two sorted list of vectors, one containing all the good
vectors and one containing the faulty ones. Next step is plotting the 
measurements that resulted in a given vector into a table, based on the sensor
readings - the way this was accomplished was to look at a given vector and then
reference the sensor readings. For example, we wanted to know the probability of
a vector given an angle - so what we did was make a table with two columns -
good and bad indicating the quality of the vector. We then referenced the
specific vector and then plotted in the two angle values used to calculate the
given vector. Doing this for each vector, we end up with a probability table.
The same method is used to construct a probability table for distance.
