\chapter{Turret Accuracy}\label{TurretAcc}
In this chapter the turrets ability to hit the target has been tested.

\section{Test Setup}
The turret is placed against a wall, and the floor is marked at 3 different
distances from the turret: 0.5m, 1m and 1.5m such that the shortest distance to
the turret is when the target is right in front of it. The target used
in the test is the final version of the target.

\section{Test Execution}
The turret is tested with the target running at three different speeds,
40\%, 50\% and 60\%. Each percentage is a measure of how much power the engines
are running at. For each speed setting, the turret is tested at the 3 different
lengths mentioned in the test setup. For each combination of speed and distance,
the test is run 4 times. The turret is placed such that it ``looks'' in the direction of
the target for every test. The target is then turned on at the speed and distance to be tested,
and then it is observed whether the turret hits or misses the target.

\section{Test Evaluation}
The result of the test can be seen in \autoref{table:accuracy}. Here it can be
seen that the turret only hits 3 out of 24 times, and in the
case of a distance of 1.5m the ultrasonic sensor would not measure a distance to
the target, and therefore no further tests at that range was conducted. But all
of the 3 shots that hit the target were from the dataset where the power was
40\% and the distance 0.5m. 

\dataTable{accuracy}{Data from the accuracy test}{accuracy}

In conclusion \name had an accuracy of 12.5\%.
